Minimal trap spaces of Logical models are maximal siphons of their Petri net encoding

### 2022-05-11 cmsb22.tex
Tables

\begin{table}[!htb]
  \caption{Timing comparisons between the proposed method and PyBoolNet on the PyBoolNet's repository.
    Column \(n\) denotes the numbers of nodes of each model. Column \(|M|\) denotes the number of minimal trap spaces and for each method is given the computation time in seconds.
    ``DNF'' means that the method did not finish the computation (with a maximum of 1000 trap spaces) within the timeout of 2 minutes. A number in bold indicates a ratio greater than three.}
  \centering
  \label{tab:pyboolnet_repo}
  \begin{tabular}{lrrrrrr}
    \toprule
    model & $n$ & $|M|$ & PyBoolNet (s) & Trappist (s) \\ \midrule
    arellano\_rootstem & 9 & 4 & 0.04 & \textbf{0.31}\\
    calzone\_cellfate & 28 & 27 & 0.03 & 0.08\\
    dahlhaus\_neuroplastoma & 23 & 32 & 0.04 & 0.11\\
    davidich\_yeast & 10 & 12 & 0.03 & 0.08\\
    dinwoodie\_life & 15 & 7 & 0.03 & 0.08\\
    dinwoodie\_stomatal & 13 & 1 & 0.04 & 0.05\\
    faure\_cellcycle & 10 & 2 & 0.04 & 0.04\\
    grieco\_mapk & 53 & 18 & 0.04 & 0.08\\
    irons\_yeast & 18 & 1 & 0.05 & 0.04\\
    jaoude\_thdiff & 103 & 1000+ & \textbf{1.73} & 0.40\\
    klamt\_tcr & 40 & 8 & 0.06 & 0.04\\
    krumsiek\_myeloid & 11 & 6 & 0.03 & 0.03\\
    multivalued & 13 & 4 & 0.02 & 0.02\\
    n12c5 & 11 & 5 & \textbf{34.37} & 0.06\\
    n3s1c1a & 2 & 2 & 0.02 & 0.03\\
    n3s1c1b & 2 & 2 & 0.02 & 0.03\\
    n5s3 & 4 & 3 & 0.03 & 0.03\\
    n6s1c2 & 5 & 3 & 0.03 & 0.04\\
    n7s3 & 6 & 3 & 0.02 & 0.02\\
    raf & 3 & 2 & 0.03 & 0.02\\
    randomnet\_n15k3 & 15 & 3 & 0.04 & 0.05\\
    randomnet\_n7k3 & 7 & 10 & 0.03 & \textbf{0.19}\\
    remy\_tumorigenesis & 34 & 25 & \textbf{1.79} & 0.13\\
    saadatpour\_guardcell & 13 & 1 & 0.02 & 0.03\\
    selvaggio\_emt & 56 & 1000+ & \textbf{1.03} & 0.23\\
    tournier\_apoptosis & 12 & 3 & 0.05 & 0.06\\
    xiao\_wnt5a & 7 & 4 & 0.06 & 0.03\\
    zhang\_tlgl & 60 & 156 & 0.26 & 0.17\\
    zhang\_tlgl\_v2 & 60 & 258 & 0.19 & 0.17\\
    \bottomrule
  \end{tabular}
\end{table}

@@

@@

    mast-cell-activation~\cite{aghamiri2020automated} & 73 & 19 & 1000+ & 0.64 & 0.15 & DNF\\

@@

    Corral-ThIL-17-diff~\cite{corral2021interplay} & 92 & 16 & 1000+ & DNF & 0.38 & DNF\\

@@

    interferon-1~\cite{ostaszewski2021covid19} & 121 & 55 & 1000+ & 8.36 & 0.19 & DNF\\

@@

    signal-transduction-in-fibroblasts~\cite{helikar2008emergent} & 139 & 9 & 1000+ & DNF & 0.56 & DNF\\
    HMOX-1-pathway~\cite{ostaszewski2021covid19} & 145 & 56 & 1000+ & 5.16 & 0.18 & DNF\\
    kynurenine-pathway~\cite{ostaszewski2021covid19} & 150 & 72 & 1000+ & DNF & 0.74 & DNF\\
    virus-replication-cycle~\cite{ostaszewski2021covid19} & 154 & 25 & 1000+ & DNF & 0.19 & DNF\\
    immune-system~\cite{DBLP:journals/bmcsb/HelikarKMBRMWSLR12} & 164 & 13 & 1000+ & DNF & 0.67 & DNF\\
    RA-apoptosis~\cite{aghamiri2020automated} & 180 & 59 & 1000+ & DNF & 0.16 & DNF\\
    MAPK~\cite{aghamiri2020automated} & 181 & 37 & 1000+ & 68.62 & 0.64 & DNF\\
    er-stress~\cite{ostaszewski2021covid19} & 182 & 75 & 1000+ & 28.65 & 0.21 & DNF\\

@@

    T-cell-check-point~\cite{hernandez2020computational} & 218 & 14 & 1000+ & 37.40 & 0.35 & DNF\\
    ErbB-receptor-signaling~\cite{helikar2013comprehensive} & 247 & 22 & 1000+ & DNF & 1.07 & DNF\\
    signaling-macrophage-activation~\cite{DBLP:journals/bmcsb/HelikarKMBRMWSLR12} & 321 & 19 & 1000+ & 15.82 & 0.63 & DNF\\
    cholocystokinin~\cite{aghamiri2020automated} & 383 & 74 & 1000+ & 1.22 & 0.73 & DNF\\
    Alzheimer~\cite{aghamiri2020automated} & 762 & 237 & 1000+ & DNF & 1.03 & DNF\\
    KEGG-network~\cite{DBLP:journals/bmcsb/Kwon16} & 1659 & 521 & 1000+ & DNF & 44.85 & DNF\\
    human-network~\cite{kim2011reduction} & 1953 & 669 & 1000+ & DNF & 42.97 & DNF\\

>>>>

\begin{table}[!htb]
  \caption{Timing comparisons between the proposed method and PyBoolNet on the PyBoolNet's repository.
    Column \(n\) denotes the numbers of nodes of each model, column \(|M|\) denotes the number of minimal trap spaces and for each method is given the computation time in seconds.
    A number in bold indicates a ratio greater than three.}
  \centering
  \label{tab:pyboolnet_repo}
  \begin{tabular}{lrrrrrr}
    \toprule
    model & $n$ & $|M|$ & PyBoolNet & Trappist \\ \midrule
    arellano\_rootstem & 9 & 4 & 0.04 & \textbf{0.31}\\
    calzone\_cellfate & 28 & 27 & 0.03 & 0.08\\
    dahlhaus\_neuroplastoma & 23 & 32 & 0.04 & 0.11\\
    davidich\_yeast & 10 & 12 & 0.03 & 0.08\\
    dinwoodie\_life & 15 & 7 & 0.03 & 0.08\\
    dinwoodie\_stomatal & 13 & 1 & 0.04 & 0.05\\
    faure\_cellcycle & 10 & 2 & 0.04 & 0.04\\
    grieco\_mapk & 53 & 18 & 0.04 & 0.08\\
    irons\_yeast & 18 & 1 & 0.05 & 0.04\\
    jaoude\_thdiff & 103 & >1000 & \textbf{1.73} & 0.40\\
    klamt\_tcr & 40 & 8 & 0.06 & 0.04\\
    krumsiek\_myeloid & 11 & 6 & 0.03 & 0.03\\
    multivalued & 13 & 4 & 0.02 & 0.02\\
    n12c5 & 11 & 5 & \textbf{34.37} & 0.06\\
    n3s1c1a & 2 & 2 & 0.02 & 0.03\\
    n3s1c1b & 2 & 2 & 0.02 & 0.03\\
    n5s3 & 4 & 3 & 0.03 & 0.03\\
    n6s1c2 & 5 & 3 & 0.03 & 0.04\\
    n7s3 & 6 & 3 & 0.02 & 0.02\\
    raf & 3 & 2 & 0.03 & 0.02\\
    randomnet\_n15k3 & 15 & 3 & 0.04 & 0.05\\
    randomnet\_n7k3 & 7 & 10 & 0.03 & \textbf{0.19}\\
    remy\_tumorigenesis & 34 & 25 & \textbf{1.79} & 0.13\\
    saadatpour\_guardcell & 13 & 1 & 0.02 & 0.03\\
    selvaggio\_emt & 56 & >1000 & \textbf{1.03} & 0.23\\
    tournier\_apoptosis & 12 & 3 & 0.05 & 0.06\\
    xiao\_wnt5a & 7 & 4 & 0.06 & 0.03\\
    zhang\_tlgl & 60 & 156 & 0.26 & 0.17\\
    zhang\_tlgl\_v2 & 60 & 258 & 0.19 & 0.17\\
    \bottomrule
  \end{tabular}
\end{table}

@@

\setlength{\tabcolsep}{4pt}

@@

    mast-cell-activation~\cite{aghamiri2020automated} & 73 & 19 & >1000 & 0.64 & 0.15 & DNF\\

@@

    Corral-ThIL-17-diff~\cite{corral2021interplay} & 92 & 16 & >1000 & DNF & 0.38 & DNF\\

@@

    interferon-1~\cite{ostaszewski2021covid19} & 121 & 55 & >1000 & 8.36 & 0.19 & DNF\\

@@

    signal-transduction-in-fibroblasts~\cite{helikar2008emergent} & 139 & 9 & >1000 & DNF & 0.56 & DNF\\
    HMOX-1-pathway~\cite{ostaszewski2021covid19} & 145 & 56 & >1000 & 5.16 & 0.18 & DNF\\
    kynurenine-pathway~\cite{ostaszewski2021covid19} & 150 & 72 & >1000 & DNF & 0.74 & DNF\\
    virus-replication-cycle~\cite{ostaszewski2021covid19} & 154 & 25 & >1000 & DNF & 0.19 & DNF\\
    immune-system~\cite{DBLP:journals/bmcsb/HelikarKMBRMWSLR12} & 164 & 13 & >1000 & DNF & 0.67 & DNF\\
    RA-apoptosis~\cite{aghamiri2020automated} & 180 & 59 & >1000 & DNF & 0.16 & DNF\\
    MAPK~\cite{aghamiri2020automated} & 181 & 37 & >1000 & 68.62 & 0.64 & DNF\\
    er-stress~\cite{ostaszewski2021covid19} & 182 & 75 & >1000 & 28.65 & 0.21 & DNF\\

@@

    T-cell-check-point~\cite{hernandez2020computational} & 218 & 14 & >1000 & 37.40 & 0.35 & DNF\\
    ErbB-receptor-signaling~\cite{helikar2013comprehensive} & 247 & 22 & >1000 & DNF & 1.07 & DNF\\
    signaling-macrophage-activation~\cite{DBLP:journals/bmcsb/HelikarKMBRMWSLR12} & 321 & 19 & >1000 & 15.82 & 0.63 & DNF\\
    cholocystokinin~\cite{aghamiri2020automated} & 383 & 74 & >1000 & 1.22 & 0.73 & DNF\\
    Alzheimer~\cite{aghamiri2020automated} & 762 & 237 & >1000 & DNF & 1.03 & DNF\\ \midrule
    KEGG-network~\cite{DBLP:journals/bmcsb/Kwon16} & 1659 & 521 & >1000 & DNF & 44.85 & DNF\\
    human-network~\cite{kim2011reduction} & 1953 & 669 & >1000 & DNF & 42.97 & DNF\\
